Tor's Usability for Censorship Circumvention

### 2015-10-05 paper/circumvention-experiment.tex
updated the list of tasks section

\documentclass{sig-alternate-hotpets15}
\usepackage{color}
\usepackage[hyphens]{url}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{pdfpages}

@@

% is the abstract missing some oomph? 
% I don't know how much the storyline is showing through.. or what we are testing. 
\begin{abstract}

@@

\noindent {\bfseries List of Tasks} 
The tasks below were originally inspired by the top Alexa sites, 
an indication of representative and relevant browsing behavior. 
We then selected sites which were commonly censored and 
refined the tasks to remove ethical concerns, such as tasks 
which would require a participant to reveal private information 
(such as login information). We hope the resulting tasks convey an idea 
of sites which are censored today, while remaining representative 
of how a user might browse the Internet.

All participants will be given the same set of tasks, 
regardless of the censorship environment. 
Although every participant will attempt the same set of tasks, 
the difficulty of completing these tasks will vary based on 
their chosen censorship environment. 
The tasks are not all intended to be challenging to complete. 
Some may not even require the use or Tor Browser, 
depending on the environment.

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item Do a Google web search.
\item Watch a YouTube video.
\item Find the Amazon best-selling books.
\item Find Yahoo's exchange rate between dollars and euros.
\item Read the Wikipedia featured article.
\item Find the Twitter trending topics.
\item Find directions on Bing Maps.
\end{itemize}

\noindent {\bfseries Experiment Execution Details} 
We plan to recruit up to 200 users for the purpose of this study, 
making it largest user study to date examining Tor (check this). 
This study will be conducted at the Experimental Social Science Laboratory (Xlab)
at the University of California, Berkeley, which consists of 36 laptops with 
cubicle walls separating each laptop. We will use individual host firewalls to simulate
the censorship environments and will write a browser extension to 
log when user activity, such as what websites they were successfully able to visit. 
The total length of the experiment, including briefing, completing the censorship 
circumvention tasks, exit survey, and debriefing, will take less than an hour. 
Participants will be compensated \$30 for their time, 
which is more to cover minimum wage and transportation costs.  \\

>>>>

\documentclass{template}
\usepackage{color}
\usepackage[hyphens]{url}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{pdfpages}

@@

\begin{abstract}

@@

\noindent {\bfseries List of Tasks} 
In our experimental setup, successful completion of 
these given tasks requires of correct configuration.
The difficulty of circumventing  censorship to visit the 
websites required for the tasks will vary on the 
simulated censorship environment. Since all participants will be given the 
same set of tasks, regardless of the censorship environment, 
the difficulty of completing the tasks remains constant assuming
correct configuration. The tasks themselves are not intended to
be challenging.

The tasks were initially inspired by the top Alexa sites, 
an indication of representative and relevant browsing behavior. 
From these, we selected sites which were commonly censored, 
but filtered tasks that would require a participant to reveal private information 
(such as login information) for ethical considerations. These tasks
were further refined after performing a pilot study of the experiment. 
We hope the tasks convey an example of how of a user might 
browse the Internet in a censored environment.

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item Do a Google web search for the population of Zimbabwe. 
\item On Youtube, find a video playing Bach's ``Ode to Joy.'' 
\item Find the Amazon best-sellers in the ``Movies \& TV'' category.
\item On Yahoo, find the exchange rate between dollars and euros.
\item In the Wikipedia ``History'' portal, click on the featured article. 
\item On Twitter, find the currently trending topics.
\item On Bing Maps, find directions from Time Square to Carnegie Hall.
\end{itemize}

\noindent {\bfseries Experiment Execution Details} 
We plan to recruit from 200 users for the purpose of this study, 
making it largest user study to date examining Tor. 
This study will be conducted at the Experimental Social Science Laboratory (Xlab)
at the University of California, Berkeley, which consists of 36 laptops with 
cubicle walls separating each laptop. We will use individual host firewalls to simulate
the censorship environments and will write a browser extension to 
log when user activity, such as what websites they were successfully able to visit. 
The total length of the experiment, including briefing, completing the censorship 
circumvention tasks, exit survey, and debriefing, will take less than an hour. 
Participants will be compensated \$30 for their time, 
which is more to cover minimum wage and transportation costs.  \\
